|

### 2025-05-05 doc/paper.qmd
Added a figure template

## Results {#sec-results1}
This section presents the replication results, comparing them with the original @ by @ball_how_2008.

>>>>

## Results {#sec-results1}
This section presents the replication results, comparing them with the original \ref{fig:fig1_original} by @ball_how_2008.

```{=latex}
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.95\textwidth]{fig1_original.pdf}
  \caption{Original Figure 1 from Ball and Shivakumar (2008)}
  \label{fig:fig1_original}
\end{figure}
```
